% Jason R. Blevins - Curriculum Vitae
%
% Copyright (C) 2004-2013 Jason R. Blevins
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely.  No attribution is
% required in any resulting documents.  I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[10pt]{article}%,letterpaper]{article}
\title{Resume}

% Jason R. Blevins - Curriculum Vitae
%
% Copyright (C) 2004-2013 Jason R. Blevins
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely.  No attribution is
% required in any resulting documents.  I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{url}
\usepackage{fontspec}
\usepackage{fontawesome}


% Fonts
\usepackage[T1]{fontenc}
\usepackage[urw-garamond]{mathdesign}

% Set your name here
\def\name{Pradyumna Shembekar}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name: Pradyumna},
  pdfkeywords = {front-end, back-end, software, new grad, university, university grad, junior, fresh, ruby on rails, C, web development},
  pdftitle = {\name: Resume},
  pdfsubject = {Resume},
  pdfpagemode = UseNone
}

\geometry{
  body={7.5in, 10.0in},
  left=0.5in,
  top=0.5in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

%% Make lists without bullets and compact spacing
%\renewenvironment{itemize}{
%  \begin{list}{}{
%    \setlength{\leftmargin}{1.5em}
%    \setlength{\itemsep}{0.1em}
%    \setlength{\parskip}{0pt}
%    \setlength{\parsep}{0.1em}
%  }
%}{
%  \end{list}
%}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\bigskip

\begin{minipage}[t]{0.495\textwidth}

  603 N Mentor Avenue\\
  Pasadena, CA 91106\\ \textbf{Phone}: (323) 597-9301
\end{minipage}
\begin{minipage}[t]{0.495\textwidth}
  \textbf{Email}: \href{mailto:pshembe@calstatela.edu}{\tt{pshembe@calstatela.edu}} \\ \textbf{Github}: \href{https://github.com/pradyumna2905}{\tt{github.com/pradyumna2905}} \\ \textbf{Linkedin}: \href{https://www.linkedin.com/in/pradyumnashembekar}{\tt{linkedin.com/in/pradyumnashembekar}}
\end{minipage}

\section*{Education}

\begin{tabular}{llll}
  \textbf{M.S.}, Electrical and Computer Engineering & California State University, Los Angeles & \textbf{June 2016} & \textbf{3.5/4.0} \\
  B.E., Electronics and Telecommunication Engineering & Gujarat Technological University & May 2013 \\
\end{tabular}

\section*{Work Experience}

\begin{itemize} \setlength{\parskip}{0.5pt} 
    
    \item \textbf{Web Developer - Intern, \textit{Aflac Inc, Los Angeles, Aug 2015 - December 2015}}
    
		Created a recruitment website in PHP using elegant MVC design patterns. Integrated with Wordpress and developed a tablet and mobile version. Implemented efficient JavaScript for better response time. Communicated with the HR and design team to meet up with their requirements.
    
    \item \textbf{Text Transcriber, \textit{California State University, Los Angeles, Aug 2014 - March 2016}}
        
        Transcribed textbooks into accessible formats on Kurzweil and Omnipage. Developed an accessible form in PHP for disabled students to submit requests for books online.
        
\end{itemize}

\section*{Independent Projects (selected)}

\begin{itemize} \setlength{\parskip}{0.5pt}

\item \textbf{Reps \& Sets}  \href{https://repsandsets.herokuapp.com/}{\tt{\faLink}}

Built a web-application to track your workouts and calculate your progress. Users can sign-up, search and follow friends, compare workouts with their friends and family. The app displays a graphical interpretation of the user's workouts' summary. A \textbf{Behavior Driven Development (BDD)} approach with automated testing using \textbf{RSpec}, \textbf{Capybara}, and \textbf{Guard} testing suites. Deployed to \textbf{Heroku}. \textbf{(Ruby on Rails)}

\item \textbf{Belly Bites}  \href{https://bellybites.herokuapp.com/}{\tt{\faLink}}

A web-application to browse and create recipes. Users have the ability to sign up, up-vote recipes, add their own recipes, and check recipes added by other chefs. A \textbf{Test-Driven-Development (TDD)} approach, back-end framework in \textbf{Ruby on Rails}, and \textbf{SQLite} as database. Deployed to \textbf{Heroku}. \textbf{(Ruby on Rails)}

\item \textbf{Modified MIPS Lite (MML) Multi-cycle Design (3 members)}  \\
Designed multi-cycle datapath and the finite state machine for MML. Programmed ALU, clock generator, and contributed towards Main Controller. Played the role of a Lead Test Engineer, responsible for setting benchmark values for various modules. Simulated and tested use cases through \textbf{Xillix} software. \textbf{(MIPS, Verilog)}

 
\item \textbf{Rice Rocks}  \href{http://www.codeskulptor.org/#user38_DZUIDXywMeaZ0Wx_5.py}{\tt{\faLink}}

Built a web-based classic arcade game of a spaceship shooting missiles at rocks. Part of Coursera's course on Interactive Programming in Python. \textbf{(Python)}


\item \textbf{Car Automation System} 

Created an application to detect open doors and engine state of a car and display messages on LCD. Used Motorolla 68HC11A8 micro-controller and simulated using \textbf{ThrSim11}. \textbf{(C, MIPS)}
\end{itemize}

\section*{Awards}

\begin{itemize} \setlength{\parskip}{0.5pt}

\item \textbf{Woman's Health Alliance - Hackathon 2015} \\
\textbf{Runners up} team (6 members)\\
Developed a web app to calculate a woman's risk of having a Cardio Vascular Disease (CVD) by setting threshold values obtained from cardiologists.
        
\end{itemize}

\section*{Skills}

\begin{itemize}
  \item Languages: \textbf{C}, \textbf{C++}, JavaScript, PHP, \textbf{Python}, \textbf{Ruby}, \textbf{Swift}

\end{itemize}


\end{document}